---
title: "M3 guitar tuning"
subtitle: "An introduction and many chord examples"
author: "Lucio Cornejo"
date: "`r Sys.time()`"
execute:
  echo: false
  cache: true
format:
  html:
    theme: custom.scss
    toc: TRUE
    toc-depth: 3 
    toc-location: left
    smooth-scroll: true
    include-after-body: scripts.html
---

\

```{r}
contador <- 0
contador_string <- ""
```

<audio class="notes" preload="auto">
  <source src="audio/D3.mp3"></source> <!--a-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Eb3.mp3"></source> <!--b-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/E3.mp3"></source> <!--c-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/F3.mp3"></source> <!--d-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Gb3.mp3"></source> <!--e-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/G3.mp3"></source> <!--f-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Ab3.mp3"></source> <!--g-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/A3.mp3"></source> <!--h-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Bb3.mp3"></source> <!--i-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/B3.mp3"></source> <!--j-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/C4.mp3"></source> <!--k-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Db4.mp3"></source> <!--l-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/D4.mp3"></source> <!--m-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Eb4.mp3"></source> <!--n-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/E4.mp3"></source> <!--o-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/F4.mp3"></source> <!--p-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Gb4.mp3"></source> <!--q-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/G4.mp3"></source> <!--r-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Ab4.mp3"></source> <!--s-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/A4.mp3"></source> <!--t-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Bb4.mp3"></source> <!--u-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/B4.mp3"></source> <!--v-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/C5.mp3"></source> <!--w-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/Db5.mp3"></source> <!--x-->
</audio>
<audio class="notes" preload="auto">
  <source src="audio/D5.mp3"></source> <!--y-->
</audio>


```{r}
#| label: "automatic-code-for-guitar-table"

library(stringr)
neck <- function(matriz,bajo,chord_name,chord_voicing) {
  m <- nrow(matriz)
  n <- ncol(matriz)

  notes <- c(
    "D3","Eb3","E3","F3",
    "Gb3","G3","Ab3","A3",
    "Bb3","B3","C4","Db4",
    "D4","Eb4","E4","F4",
    "Gb4","G4","Ab4","A4",
    "Bb4","B4","C5","Db4","D5"
  )

  tags <- c(
    "a","b","c","d",
    "e","f","g","h",
    "i","j","k","l",
    "m","n","o","p",
    "q","r","s","t",
    "u","v","w","x","y"
  )

  # Obtain note positions
  posiciones <- list()
  counter <- 0
  for (i in 1:m) {
    for (j in 1:n) {
      if(nchar(matriz[i,j])<2){
        counter <- counter + 1
        posiciones[[counter]] <- c(i,j)
      }
    }
  }
  fret <- matrix(0,m,n)
  for (i in m:1) {
    t <- 1 + 4*(m-i)
    fret[i,] <- t:(t+n-1)
  }
  filas <- NULL
  columnas <- NULL
  for (i in 1:length(posiciones)) {
    filas[i] <- posiciones[[i]][1]
    columnas[i] <- posiciones[[i]][2]
  }
  call <- cbind(filas,columnas)
  indices <- rev(fret[call])

  # Adjusting the notes to be played
  k <- length(indices)
  indices <- indices - rep(indices[1]-1,k)
  if (bajo == -1) {
    indices <- indices + rep(4*(6-m),k)  
  } else {
    indices <- indices + rep(bajo,k)
  }
  
  # Unique identifier
  id <- ""
  for (i in indices) {
    id <- paste(id,tags[i],sep="")
  }

  # Item button
  contador <<- contador + 1
  contador_string <<- paste0(as.character(contador),".") 
  item <- paste0(
    "<div style=\"white-space: nowrap;\">\n  <p>\n",
    "    <input class=\"esconde-item\" value=\"",
    contador_string, "\"type=\"button\"></input>\n"
  )
  voicing <- paste(chord_voicing, collapse = "&emsp;")
  item <- paste0(
    item, "    &ensp;**",
    chord_name, "&ensp;:&ensp;** ",
    voicing, "\n  </p>\n"
  )

  # HTML Table
  tabla <- paste0(
    item, "  <table id='", id, 
    "' class='guitar columns-", as.character(n), "'>\n"
  )
  for (i in 1:m) {
    tabla <- paste0(tabla, "    <tr>\n")
    for (j in 1:n) {
      tabla <- paste0(tabla, "      <td>", matriz[i,j], "</td>\n")
    }
    tabla <- paste0(tabla, "    </tr>\n")
  }

  # Chord notes
  tabla <- paste(tabla, "    <caption>", "Notes of the chord: ")
  chord_notes <- paste(notes[indices], collapse="&nbsp; ")
  tabla <- paste0(tabla, chord_notes)
  tabla <- paste0(tabla, "</caption>\n")
  tabla <- paste0(tabla, "  </table>\n</div>\n\n")

  # Insert HTML code for the guitar_diagram
  cat(tabla)
}
```


## About

This website serves as a tool for people interested in another approach to guitar tuning. \
<p> 
  The tuning we'll be working with in this site is called 
  <span style="text-decoration: underline; font-weight: bold;">M3 tuning</span> 
  because each string of the guitar is
  <span style="text-decoration: underline; font-weight: bold;">one major third</span> 
  apart from any consecutive string next to it.
</p>

Partly for that reason, the guitar diagrams displayed in this site are not completely similar to 
the ones guitarrists are used to. Let me show you an example of what we'll be working with: 

<p style="margin-bottom: 6x;"> &nbsp; </p>

<table class="guitar">
  <tr>
    <td>Ab4</td>
    <td>A4</td>
    <td>Bb4</td>
    <td>B4</td>
  </tr>
  <tr>
    <td>E4</td>
    <td>F4</td>
    <td>Gb4</td>
    <td>G4</td>
  </tr>
  <tr>
    <td>C4</td>
    <td>Db4</td>
    <td>D4</td>
    <td>Eb4</td>
  </tr>
  <tr>
    <td>Ab3</td>
    <td>A3</td>
    <td>Bb3</td>
    <td>B3</td>
  </tr>
  <tr>
    <td>E3</td>
    <td>F3</td>
    <td>Gb3</td>
    <td>G3</td>
  </tr>
  <tr>
    <td>C3</td>
    <td>Db3</td>
    <td>D3</td>
    <td>Eb3</td>
  </tr>
</table>

<p style="margin-bottom: 0.5px;"> &nbsp; </p>

<p> 
  As you can see, the horizontal lines in the diagram
  <span style="text-decoration: underline; font-weight: bold;">do not</span> 
  represent guitar strings. 
  Such lines are simply imaginary separators of the notes in the guitar.
  However, such diagram still represents a section of the guitar, where each
  cell/mini-rectangle denotes a note, the bottom rows of the diagram stand for
  the lower notes (frequency wise) and the top rows of the diagram stand for 
  the upper notes.
</p>

<p> 
  Note a particular
  <span style="text-decoration: underline; font-weight: bold;">symmetry</span> 
  of such M3 guitar diagram: Every note is repeated
  (with respect to octave equivalence) in the same column 
  <span style="text-decoration: underline;">three</span> 
  rows above and below in the diagram. 
</p>

<p> 
  Such symmetry allows any guitar of six strings tuned with the M3 tuning
  to be divided 
  <span style="text-decoration: underline; font-weight: bold;">equally</span> 
  (with respect to octave equivalence) into two sections:
  The group of the first three strings and the group of the last three strings. \
  So, it becomes much easier to learn the note positions along the guitar neck,
  the musical scales, chords and so on.
</p>

<p style="margin-bottom: 20px;"> &nbsp; </p>

## How to use this site

Every chord shown in this site can be heard by simply clicking on its respective diagram.

It won't be necessary to show in the diagrams the guitar strings represented by the diagram/table rows, because,
thanks to the M3 tuning symmetry discussed in the "About" section, if you transpose along the guitar neck a "hand position" shown in some 
diagram (changing fret and/or string positions), _the chord type remains the same_.

Which means that, for example, the "major 7 chord" hand position is the same everywhere in the guitar, if such guitar is tuned
with the M3 tuning^[For guitars, such property is unique to tuning systems where the musical distance between any two consecutive strings is always the same. For the M3 tuning, such musical distance is a major third.]. 

In order to see a couple chord diagram examples, press the following black buttons "-1." and "0.":

```{r}
#| results: asis

contador <- -2
chord <- matrix("&nbsp; &nbsp;",6,3)
chord[6,3]   <- 0  #"&nbsp; &nbsp;"
chord[4,3]  <- 4 #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 2 #"&nbsp; &nbsp;"
chord[1,2] <- 3 #"&nbsp; &nbsp;"
neck(chord,0,"maj9",c("3","1","9","5","7"))
```
\
```{r}
#| results: asis

contador <- -1
chord <- matrix("&nbsp; &nbsp;",6,4)
chord[6,2]   <- 2  #"&nbsp; &nbsp;"
chord[4,4]  <- 3 #"&nbsp; &nbsp;"
chord[3,4] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1 #"&nbsp; &nbsp;"
chord[1,1] <- 1 #"&nbsp; &nbsp;"
neck(chord,2,"min9",c("1","b7","9","b3","5"))
```
\

Contrary to the chord diagram example in the "About" section, from now on the chord diagrams in this site can only contain
the numbers 0, 1, 2, 3 and 4 (no notes whatsoever), associated in that specific order to the fingers thumb, index, middle, ring and pinky. 
Besides this, each diagram will have a caption displaying the notes that sound when you click on such diagram.

Also, the chords will be presented as:

<p>"Button displaying the current number in the chords list" &ensp; "Chord name" <strong style="font-weight: bold;">:</strong> &ensp; "Chord voicing"</p>

The chord voicing will be based on the degrees of the notes, presented (frequency wise) from lowest to highest.

<p style="margin-bottom: 7px;"> &nbsp; </p>

Lastly, by default all the chords in this website are hidden when the site loads, but you may display them all, or hide all of them, 
by pressing the appropiate button out of the following two:
<!--#endregion-->

<!--#region Show or hide all chord diagrams -->
<input class="universal-button" type="button" value="Hide all chord diagrams" onclick="esconder()"></input>
<p style="margin-bottom: 10px;"> &nbsp; </p>
<input class="universal-button" type="button" value="Show all chord diagrams" onclick="mostrar()"></input>

<script>
  let tablas = document.getElementsByClassName('guitar');
  function esconder () { 
    for (let i = 1; i < tablas.length; i++) { tablas[i].style.display = 'none'; }
  }
  function mostrar (){ 
    for (let i = 1; i < tablas.length; i++) { tablas[i].style.display = 'table'; }
  }
</script>

<p style="margin-bottom: 10px;"> &nbsp; </p>

```{r}
contador <<- 0
contador_string <<- ""
```

## 3-string chords

### Major {.major}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,2)
chord[3,2] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 3 #"&nbsp; &nbsp;"
chord[1,1] <- 2 #"&nbsp; &nbsp;"
neck(chord,10,"maj",c("1","3","5"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,2)
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,2] <- 3  #"&nbsp; &nbsp;"
neck(chord,6,"maj",c("5","1","3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,2)
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 3  #"&nbsp; &nbsp;"
neck(chord,4,"maj",c("3","5","1"))
```
\

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,4)
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,1] <- 1 #"&nbsp; &nbsp;"
chord[1,4] <- 4 #"&nbsp; &nbsp;"
neck(chord,4,"maj7 (no 5)",c("1","3","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,4)
chord[3,4] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"maj7 (no 5)",c("7","1","3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,4)
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,4] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,5,"maj7 (no 5)",c("3","7","1"))
```
\

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,5)
chord[3,5] <- 4 #"&nbsp; &nbsp;"
chord[2,3] <- 2  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,11,"maj add9 (no 5)",c("1","9","3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,5)
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,5] <- 4  #"&nbsp; &nbsp;"
chord[1,3] <- 2  #"&nbsp; &nbsp;"
neck(chord,4,"maj add9 (no 5)",c("3","1","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,3] <- 3  #"&nbsp; &nbsp;"
neck(chord,4,"7 (no 5)",c("1","3","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,5,"7 (no 5)",c("3","b7","1"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,10,"7 (no 5)",c("b7","1","3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,3] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,6,"maj add(#11) (no 5)",c("1","3","#11"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,3] <- 4  #"&nbsp; &nbsp;"
neck(chord,11,"maj add(#11) (no 5)",c("3","#11","1"))
```
\

### Suspended {.suspended}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,8,"sus4",c("1","4","5"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,3)
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 2  #"&nbsp; &nbsp;"
neck(chord,10,"sus2",c("1","2","5"))
```
\

### Minor {.minor}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",3,2)
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,8,"min",c("1","b3","5"))
```
\


## 4-string chords

### Major {.major}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,2)
chord[4,2] <- 3  #"&nbsp; &nbsp;"
chord[3,2] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 2  #"&nbsp; &nbsp;"
neck(chord,5,"maj7",c("1","3","5","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,4] <- 3  #"&nbsp; &nbsp;"
chord[3,4] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,4,"maj7",c("5","7","1","3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,5)
chord[4,4] <- 3  #"&nbsp; &nbsp;"
chord[3,5] <- 4 #"&nbsp; &nbsp;"
chord[2,3] <- 2  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,6,"maj add9",c("5","1","9","3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,3] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"maj add9",c("3","5","1","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,2] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,8,"maj add9",c("1","3","5","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,3] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,3,"maj add(#11)",c("5","1","3","#11"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,3] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 2  #"&nbsp; &nbsp;"
neck(chord,10,"maj7 add(#11)",c("1","3","#11","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,3] <- 2  #"&nbsp; &nbsp;"
chord[3,4] <- 3 #"&nbsp; &nbsp;"
chord[2,4] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,4,"maj add(11)",c("5","1","3","4"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,2)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,2] <- 3 #"&nbsp; &nbsp;"
chord[2,2] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"maj7 #5",c("1","3","#5","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,4] <- 3  #"&nbsp; &nbsp;"
chord[3,4] <- 4 #"&nbsp; &nbsp;"
chord[2,3] <- 2  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,10,"major add(13)",c("1","3","5","6"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,3] <- 3  #"&nbsp; &nbsp;"
neck(chord,7,"maj 6/9",c("1","3","6","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,5)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,4] <- 3 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,5] <- 4  #"&nbsp; &nbsp;"
neck(chord,7,"maj add(13)",c("1","5","6","3"))
```
\

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,3] <- 4 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,8,"7",c("1","3","5","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,2] <- 2  #"&nbsp; &nbsp;"
neck(chord,6,"7 add(b9)",c("1","3","b7","b9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,3] <- 4  #"&nbsp; &nbsp;"
neck(chord,10,"9",c("1","3","b7","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,5,"7 add(#9)",c("1","3","b7","#9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,3] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"7 (b5)",c("1","3","b5","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,4] <- 3  #"&nbsp; &nbsp;"
chord[3,4] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 2  #"&nbsp; &nbsp;"
neck(chord,7,"7 add(11)",c("1","3","4","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,4] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,6,"rootless 7 add(11)",c("5","b7","3","11"))
```
\

### Suspended {.suspended}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,3] <- 4  #"&nbsp; &nbsp;"
neck(chord,6,"sus2",c("1","2","5","1"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 4  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,2] <- 3  #"&nbsp; &nbsp;"
neck(chord,5,"maj7 sus2",c("1","2","5","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,3] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 3  #"&nbsp; &nbsp;"
neck(chord,6,"sus4",c("1","4","5","1"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"maj7 sus4",c("1","4","5","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,4] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,6,"sus2 add(#11)",c("1","#11","5","9"))
```
\


```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,4] <- 4  #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,4,"7 sus4",c("1","4","5","b7"))
```
\

### Minor {.minor}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 4  #"&nbsp; &nbsp;"
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,2] <- 3  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"min7",c("1","b3","5","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,2)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,1] <- 1  #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,5,"min add(M7)",c("1","b3","5","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,1] <- 1  #"&nbsp; &nbsp;"
chord[2,4] <- 4  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,5,"min9",c("1","b3","b7","9"))
```
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,2] <- 3 #"&nbsp; &nbsp;"
chord[2,3] <- 4  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,3,"min add(9)",c("b3","5","1","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,1] <- 1  #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,7,"min add(9)",c("1","b3","5","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,4] <- 4  #"&nbsp; &nbsp;"
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 2  #"&nbsp; &nbsp;"
neck(chord,7,"min7 add(11)",c("1","b3","11","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,4] <- 4 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,3] <- 3  #"&nbsp; &nbsp;"
neck(chord,5,"min7 add(11)",c("b3","b7","1","11"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,4] <- 4  #"&nbsp; &nbsp;"
chord[3,3] <- 2 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,7,"min add(13)",c("1","b3","5","6"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,3] <- 3  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,5,"min 6/9",c("1","b3","6","9"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,4] <- 3 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,4,"min add(13)",c("1","5","6","b3"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,2] <- 2 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,9,"min7b5",c("1","b3","b5","b7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,3)
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,3] <- 4  #"&nbsp; &nbsp;"
chord[1,2] <- 3  #"&nbsp; &nbsp;"
neck(chord,10,"min (b5) = dim",c("1","b3","b5","1"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,4] <- 4  #"&nbsp; &nbsp;"
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,11,"dim7",c("1","b3","b5","bb7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",4,4)
chord[4,1] <- 1  #"&nbsp; &nbsp;"
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,2] <- 2  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,9,"dim7",c("1","b5","bb7","b3"))
```
\


## 5-string chords

### Major {.major}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",5,3)
chord[5,3] <- 3  #"&nbsp; &nbsp;"
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,3] <- 4 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,6,"maj (9,#11)",c("3","5","1","9","#11"))
```
\


### Suspended {.suspended}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",5,4)
chord[5,1] <- 1  #"&nbsp; &nbsp;"
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,3] <- 3 #"&nbsp; &nbsp;"
chord[2,4] <- 4  #"&nbsp; &nbsp;"
chord[1,4] <- 4  #"&nbsp; &nbsp;"
neck(chord,5,"min add(11)",c("1","11","b7","b3","5"))
```
\


### Minor {.minor}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",5,3)
chord[5,3] <- 4  #"&nbsp; &nbsp;"
chord[4,2] <- 2  #"&nbsp; &nbsp;"
chord[3,2] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1  #"&nbsp; &nbsp;"
chord[1,1] <- 1  #"&nbsp; &nbsp;"
neck(chord,4,"min9",c("1","b3","5","b7","9"))
```
\


## 6-string chords

### Major {.major}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",6,3)
chord[6,3] <- 0 #"&nbsp; &nbsp;"
chord[5,2] <- "&nbsp; &nbsp;"
chord[4,3] <- 4 #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 2 #"&nbsp; &nbsp;"
chord[1,2] <- 3 #"&nbsp; &nbsp;"
neck(chord,3,"maj9",c("3","1","9","5","7"))
``` 
\ 
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",6,3)
chord[6,2] <- 2 #"&nbsp; &nbsp;"
chord[5,2] <- "&nbsp; &nbsp;"
chord[4,1] <- 1 #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,2] <- 3 #"&nbsp; &nbsp;"
chord[1,3] <- 4 #"&nbsp; &nbsp;"
neck(chord,3,"maj7 add(13)",c("1","5","7","3","13"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",6,4)
chord[6,1] <- 1 #"&nbsp; &nbsp;"
chord[5,4] <- 3 #"&nbsp; &nbsp;"
chord[4,3] <- "&nbsp; &nbsp;"
chord[3,3] <- 2 #"&nbsp; &nbsp;"
chord[2,1] <- 1 #"&nbsp; &nbsp;"
chord[1,4] <- 4 #"&nbsp; &nbsp;"
neck(chord,1,"maj9",c("1","5","9","3","7"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",5,3)
chord[5,3] <- 3 #"&nbsp; &nbsp;"
chord[4,1] <- 1 #"&nbsp; &nbsp;"
chord[3,1] <- 1 #"&nbsp; &nbsp;"
chord[2,1] <- 1 #"&nbsp; &nbsp;"
chord[1,1] <- 1 #"&nbsp; &nbsp;"
neck(chord,8,"7 (no 5) add(b13)",c("b7","1","3","b13","1"))
```
\
```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",6,3)  
chord[6,3] <- 3 #"&nbsp; &nbsp;"  
chord[5,3] <- 4 #"&nbsp; &nbsp;"  
chord[4,2] <- 2 #"&nbsp; &nbsp;"  
chord[3,1] <- 1 #"&nbsp; &nbsp;"  
chord[2,1] <- 1 #"&nbsp; &nbsp;"  
chord[1,1] <- 1 #"&nbsp; &nbsp;"  
neck(chord,4,"9 add(#11)",c("1","3","5","b7","9","#11")) 
```
\

### Suspended {.suspended}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",6,3)
chord[6,1] <- 0  #"&nbsp; &nbsp;"
chord[4,3] <- 3  #"&nbsp; &nbsp;"
chord[3,3] <- 4 #"&nbsp; &nbsp;"
chord[2,2] <- 1  #"&nbsp; &nbsp;"
chord[1,2] <- 2  #"&nbsp; &nbsp;"
neck(chord,0,"13 sus4",c("1","b7","9","11","13"))
```
\


### Minor {.minor}

```{r}
#| results: "asis"

chord <- matrix("&nbsp; &nbsp;",6,4)
chord[6,2] <- 2 #"&nbsp; &nbsp;"
chord[5,2] <- "&nbsp; &nbsp;"
chord[4,1] <- 1 #"&nbsp; &nbsp;"
chord[3,4] <- 3 #"&nbsp; &nbsp;"
chord[2,1] <- 1 #"&nbsp; &nbsp;"
chord[1,4] <- 4 #"&nbsp; &nbsp;"
neck(chord,2,"min9",c("1","5","9","b3","b7"))
```
\


## 7-string chords

### Major {.major}


### Suspended {.suspended}


### Minor {.minor}

<p style="margin-bottom: 50px;"> &nbsp; </p>

<!--#region  Play every chord in this website: one second wait between chords -->
  <!-- Pending to create an input button which allows the user to set a time between chords and then play them all automatically.   -->
  <!-- <script>
    const delay = ms => new Promise(resolve => setTimeout(resolve, ms));
    await delay(1000); /// waiting 1 second.

    let acordes = document.getElementsByClassName('guitar');
    for(var i=1;i<acordes.length;i++){
    acordes[i].click();
    await delay(1000);
    }
  </script> -->